\documentclass[11pt,a4paper,openany]{article}

\def\baselinestretch{1}
\pagenumbering{arabic}

\makeatletter
\newcommand{\rmnum}[1]{\romannumeral #1}
\newcommand{\Rmnum}[1]{\expandafter\@slowromancap\romannumeral #1@}
\makeatother

\usepackage{graphicx}
\usepackage{simplemargins}
\setallmargins{1in}

\begin{document}


\begin{center}
CS6280 :: Semester Project\\ 
\textbf{Event notification system for information in web service applications
\\System Requirement Documentation\\} \textit{Tanima Dey   td8h@virginia.edu \\ Sirajum Munir  sm7hr@virginia.edu}

\end{center}

\section{Introduction}

Human mind remains pre-occupied with so many thoughts that the attention for some particular events or information may be missed out for such involvement. The events or information can be very crucial for the person, but because of being under various circumstances and stressful life style, these can go without any attention. This might result in several losses, such as, financial, personal, or social.


In today’s world, the Internet undoubtedly plays an important role which influences the lives of people at all ages irrespective of jobs, careers, positions in a company etc. All have something in their lives or works that are highly dependent on various Internet web services. Such as, electronic mail or e-mail, online banking, social networks, personal interests etc. People now-a-days read news and get weather reports from different websites rather than watching the television. Students and faculty members get important updates for their research from the vast collection of information provided in different websites. They can also know about the research conduected by other people in other universities. Internet has improved the communication through messengers, different social networks formed in web services like Facebook, Twitter, different professional networks, such as, LinkedIn etc. Whenever anyone needs any information about anything, it could be related to shopping, banking, research; studies and so on can simply run the desired string in any search engine which eventually generates a long list of search results from which the desired information can be retrieved easily. The search engines have become such an integral part of our lives that “google” has now become a buzzword. In a summary, Internet has made everyone’s life easier from every aspect.

People now-a-days manage most of their important works through different web services provided by the Internet. Appropriate and important events and news should be notified to them if they are busy elsewhere and the attention has been occupied by something else. Such notification can help them not to miss a deadline, inform them the information of their interests and overall make their lives easier.


\section{Requirements}

In this project, we design such a system which sends notification to the registered users of any information of their interests. The information can be an e-mail received from a special person, information/news updated/published in a particular website, events in social and professional networks through Facebook, Twitter, and LinkedIn etc. The notification that is sent can be of various forms. It can be an e-mail, a message or phone call through wireless telephone service or a pop-up window in a personal computer etc. 

Using our system, the users should be able to provide their preferences of information and events which they are interested in and to be notified. The interest notification can be of various categories, like, e-mail notification, notification from networking sites, notification from websites, such as, banking, news, blogs, related to hobbies, websites containing favorite songs, videos etc. The system should capture events as described by the users and send them notification by the preferred way set by the users, such as, popping up a windows if the user is logged in, sending a text message or call at the user's cell phone etc.

\section{Validation}

Validating the requirements of software system is very crucial. We can validate the system by prototyping. We deploy the system after it is developed and get the feedbacks of the users after they have used the system. They can report us back what are the functionalities that have been missing from the system, what are the features that are incomplete, the easiness of the use, their satisfaction about the system as a whole etc.

//this is verification\\
The system can be validated by similar to test cases. For example, if the user is interested about a particular news updated in a website, and the system returns some stale information, then we can conclude that the system is not doing the... 

\end{document}
